GA-based Training-Free NAS Algorithm with Hybrid Score Function

### 2023-03-13 paper/main.tex

    Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} proposed a 
    score function without the requirement for training. 
    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ mapped through a neural 
    network as $f(x_i)$. The indicator variables from each ReLU units in $f$ 
    at $x_i$ form a binary code $c_i$ that define the linear region.
    The correlation between binary codes for the whole mini-batch can be examined 
    by computing the kernel matrix
    \begin{equation}
        K_H=\begin{pmatrix}N_A-d_H(c_1,c_2)&\cdots&N_A-d_H(c_1,c_N)\\\vdots&\ddots&\vdots\\N_A-d_H(c_N,c_1)&\cdots&N_A-d_H(c_N,c_1)\end{pmatrix}
    \end{equation}
    where $N_A$ is the number of ReLU units and $d_H(c_i,c_j)$ is the hamming 
    distance between the binary code $c_i$ and $c_j$.
    With the kernel matrix, the score of an architecture can be evaluate as 
    follow:
    \begin{equation}
        s=\log\lvert K_H\rvert
    \end{equation}
    The rationale behind is to see how dissimilar the linear region activated by 
    the ReLU units.

    On the other hand, Chen et al. proposed using the condition number of NTK 
    as an evaluation of the trainability, definde as
    \begin{equation}
        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
    \end{equation}
    where $\lambda_{\textrm{max}}(\hat\Theta)$ and $\lambda_{\textrm{min}}(\hat\Theta)$ 
    are the maximum and minimum eigenvalues of NTK ($\hat\Theta$) respectively.
    The rationale behind is based on the work of Lee et al. \cite{Lee_2020} and 
    Xiao et al. \cite{DBLP:journals/corr/abs-1912-13053}, which concluded briefly, 
    the training dynamics of a wide neural network can be solved as 
    \begin{equation}
        \mu_t(\textbf{X}_{\textrm{train}})=(\textbf{I}-e^{-\eta\hat\Theta_{\textrm{train}}t})\textbf{Y}_{\textrm{train}}
    \end{equation}

>>>>

    Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} proposed a 
    score function without the requirement for training. 
    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ mapped through a neural 
    network as $f(x_i)$. The indicator variables from each ReLU units in $f$ 
    at $x_i$ form a binary code $c_i$ that define the linear region.
    The correlation between binary codes for the whole mini-batch can be examined 
    by computing the kernel matrix
    \begin{equation}
        K_H=\begin{pmatrix}N_A-d_H(c_1,c_2)&\cdots&N_A-d_H(c_1,c_N)\\\vdots&\ddots&\vdots\\N_A-d_H(c_N,c_1)&\cdots&N_A-d_H(c_N,c_1)\end{pmatrix}
    \end{equation}
    where $N_A$ is the number of ReLU units and $d_H(c_i,c_j)$ is the hamming 
    distance between the binary code $c_i$ and $c_j$.
    With the kernel matrix, the score of an architecture can be evaluate as 
    follow:
    \begin{equation}
        s=\log\lvert K_H\rvert
    \end{equation}
    The rationale behind is to see how dissimilar the linear region activated by 
    the ReLU units between two inputs. An architecture shall learn better 
    when inputs are well separated.
    Later, Wu et al. \cite{10.1145/3491396.3506510}

    On the other hand, instead of using the correlation of binary activation 
    patterns as score. Chen et al. proposed using the condition number of NTK 
    as an evaluation of the trainability, defined as
    \begin{equation}
        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
    \end{equation}
    where $\lambda_{\textrm{max}}(\hat\Theta)$ and $\lambda_{\textrm{min}}(\hat\Theta)$ 
    are the maximum and minimum eigenvalues of NTK ($\hat\Theta$) respectively.
    The rationale behind is based on the work of Lee et al. \cite{Lee_2020} and 
    Xiao et al. \cite{DBLP:journals/corr/abs-1912-13053}, which concluded briefly, 
    the training dynamics of a wide neural network can be solved as 
    \begin{equation}
        \mu_t(\textbf{X}_{\textrm{train}})=(\textbf{I}-e^{-\eta\hat\Theta_{\textrm{train}}t})\textbf{Y}_{\textrm{train}}
    \end{equation}
